Non-coding RNAs of bird genomes

### 2013-07-19 paper/manuscript.tex
Writing, writing.

\title{Non-coding RNAs of bird genomes.}

@@

@@

The Vault RNA forms a major component of the vault ribonucleoprotein
complex, this is one of the largest particles found in the vertebrate
cell, it could envelope the ribosome \cite{Kong:1999}. As yet

\cite{Stadler:2009}

 Vault, 7SK, HAR1A

@@

\begin{figure}[ht]
  \includegraphics[width=0.5\textwidth]{figures/miRNA.pdf}
  \includegraphics[width=0.45\textwidth]{figures/snoRNA.pdf}
  \caption[]{.}\label{fig:3}
\end{figure}

>>>>

\title{Non-coding RNAs of bird genomes}

@@

{\bf MAY BE MOVED INTO THE lncRNA PAPER!}

@@

The Vault RNA forms a major component of the vault ribonucleoprotein
complex, this is one of the largest particles found in the vertebrate
cell; In fact, it is larger than the ribosome \cite{Kong:1999}. As yet
not much is known about the function of Vault. The Vault RNA has been
shown to be broadly conserved in metazoans \cite{Stadler:2009}.

% Vault, 7SK, HAR1A

@@

\begin{figure}[ht]
  \includegraphics[height=0.95\textheight]{figures/miRNA.pdf}
  \includegraphics[height=0.95\textheight]{figures/snoRNA.pdf}
  \caption[]{.}\label{fig:3}
\end{figure}
